Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
- tex: new CRP

@@

	Even then, the number of inequations to consider is exponential in the number
	of tasks. While it has been shown that constraints that cover intervals ending
	after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
	therefore not usable, or at least not for the purposes of this paper. The
	following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
		is not possible to directly use a solver for the CRP as in a task system,
		$T_i$ values could have common factors. However, the instance can be modified
		(each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

@@

		A better method for finding the FPDIT consists in splitting the algorithm that
		is used to solve the CRP in two separate parts. The algorithm requires
		calculating one modular inverse for each task. %TODO continue

>>>>

\algsetup{
	indent=2em,
	linenosize=\small,
	linenodelimiter=\ 
}

@@

	Even then, the number of inequations to consider is exponential in the number
	of tasks. While it has been shown that constraints that cover intervals ending
	after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
	therefore not usable, or at least not for the purposes of this paper. The
	following concept is thus introduced, which is similar to the end of the busy period but does not depend on the execution times.

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
		is not possible to directly use a solver for the CRP (such as Gauss's
		algorithm) as in a task system, $T_i$ values could have common factors.
		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

@@

		A better method for finding the FPDIT consists in splitting Gauss's algorithm
		into two separate parts. The global structure is simply a sum of factors, each
		term being dependant on which $a_i$ value is chosen. A major speedup can
		be acheived by first computing all possible terms for each task (only one
		modular inverse must be computed per task that way) then creating all possible DIT values
		by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.
